---
title: "Compute population-level posterior mean variance components"
site: workflowr::wflow_site
date: "2020-June-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      tidy='styler', tidy.opts=list(strict=FALSE,width.cutoff=100), highlight=TRUE)
```

For each of the genetic groups (GG, C1, C2, C3 , ALL):

Compute the posterior mean variances and covariances from the on-disk-stored, post-burnIn, thinned posterior samples of marker effects.

Models: **A**, **AD**, **DirDom**

For the directional dominance (**DirDom**) marker effects set. Add inbreeding/propHom effect to vector _d_.

* Compute $Var(GEBV)$ with allele sub. effects as: $\alpha = a + d(q-p)$.
* Compute $Var(GETGV) = Var(Add) + Var(Dom)$

# Models A and AD
## Set-up
```{bash, eval=F}
# activate multithread OpenBLAS
export OMP_NUM_THREADS=112
```

```{r, eval=F}
rm(list=ls()); gc()
library(tidyverse); library(magrittr); library(predCrossVar); library(BGLR);
blups<-readRDS(here::here("data","blups_forawcdata.rds")) %>% 
  select(Trait,blups) %>% # BLUPs long-->wide for multivar analysis
  unnest(blups) %>% 
  select(Trait,germplasmName,drgBLUP) %>% 
  spread(Trait,drgBLUP) %>%  # choosing de-regressed BLUPs as responses despite unweighted analysis
  select(germplasmName,all_of(c("DM","logFYLD","MCMDS","TCHART"))) # precaution to ensure consistent column order

# SNP data ------------
snps<-readRDS(here::here("data","dosages_awc.rds")) %>% 
  remove_invariant(.); dim(snps) # [1] 5591 38093

# Training datasets -----------
geneticgroups<-blups %>% 
  filter(!grepl("TMS13|TMS14|TMS15",germplasmName)) %>% 
  mutate(Group="GG") %>% 
  bind_rows(blups %>% 
              filter(grepl("TMS13",germplasmName)) %>% 
              mutate(Group="TMS13")) %>% 
  bind_rows(blups %>% 
              filter(grepl("TMS14",germplasmName)) %>% 
              mutate(Group="TMS14")) %>% 
  bind_rows(blups %>% 
              filter(grepl("TMS15",germplasmName)) %>% 
              mutate(Group="TMS15")) %>% 
  bind_rows(blups %>% 
              mutate(Group="All")) %>% 
  nest(blups=-Group) %>% 
  crossing(Model=c("A","AD")) %>% 
  mutate(blups=map(blups,~filter(.,germplasmName %in% rownames(snps))),
         outName=paste0("mt_",Group,"_",Model))

# Parallelization specs ---------
require(furrr); options(future.globals.maxSize=50000*1024^2)
plan(multiprocess); options(mc.cores=10); 

# MCMC params ------
nIter<-30000; burnIn<-5000; thin<-5

# getVarComps function -----------
## Wrapper function for getMultiTraitPMVs_A and getMultiTraitPMVs_AD
## For a given Model / data chunk, load stored posterior marker effects
## Compute vars/covars
source(here::here("code","getVarComps.R"))
```

## Compute var. comps
```{r, eval=F}
# cbsulm12 - Done!
geneticgroups %<>% 
  mutate(PMV=future_pmap(.,getVarComps,snps=snps,nIter=30000, burnIn=5000,thin=5))
saveRDS(geneticgroups,file=here::here("output","pmv_varcomps_geneticgroups.rds"))

```

# Model DirDom

## Set-up
```{bash, eval=F}
# activate multithread OpenBLAS
export OMP_NUM_THREADS=112
```

```{r, eval=F}
rm(list=ls()); gc()
library(tidyverse); library(magrittr); library(predCrossVar); library(BGLR);
blups<-readRDS(here::here("data","blups_forawcdata.rds")) %>% 
  select(Trait,blups) %>% # BLUPs long-->wide for multivar analysis
  unnest(blups) %>% 
  select(Trait,germplasmName,drgBLUP) %>% 
  spread(Trait,drgBLUP) %>%  # choosing de-regressed BLUPs as responses despite unweighted analysis
  select(germplasmName,all_of(c("DM","logFYLD","MCMDS","TCHART"))) # precaution to ensure consistent column order

# SNP data ------------
snps<-readRDS(here::here("data","dosages_awc.rds")) %>% 
  remove_invariant(.); dim(snps) # [1] 5591 38093

# Training datasets -----------
geneticgroups<-blups %>% 
  filter(!grepl("TMS13|TMS14|TMS15",germplasmName)) %>% 
  mutate(Group="GG") %>% 
  bind_rows(blups %>% 
              filter(grepl("TMS13",germplasmName)) %>% 
              mutate(Group="TMS13")) %>% 
  bind_rows(blups %>% 
              filter(grepl("TMS14",germplasmName)) %>% 
              mutate(Group="TMS14")) %>% 
  bind_rows(blups %>% 
              filter(grepl("TMS15",germplasmName)) %>% 
              mutate(Group="TMS15")) %>% 
  bind_rows(blups %>% 
              mutate(Group="All")) %>% 
  nest(blups=-Group) %>% 
  crossing(Model=c("DirDomA","DirDomAD")) %>% 
  mutate(blups=map(blups,~filter(.,germplasmName %in% rownames(snps))),
         outName=paste0("mt_",Group,"_DirectionalDom"))

# Parallelization specs ---------
require(furrr); options(future.globals.maxSize=50000*1024^2)
plan(multiprocess); options(mc.cores=10); 

# MCMC params ------
nIter<-30000; burnIn<-5000; thin<-5

# getDirectionalDomVarComps function -----------
## Wrapper function for getMultiTraitPMVs_A and getMultiTraitPMVs_AD
## For a given Model / data chunk, load stored posterior marker effects
## Compute vars/covars
source(here::here("code","getDirectionalDomVarComps.R"))
```

## Compute var. comps
```{r, eval=F}
# cbsulm12 - Done!
geneticgroups %<>% 
  mutate(PMV=future_pmap(.,getDirectionalDomVarComps,snps=snps,nIter=30000, burnIn=5000,thin=5))
saveRDS(geneticgroups,file=here::here("output","pmv_DirectionalDom_varcomps_geneticgroups.rds"))

```

# Process results

## Tidy VarComps 

```{r, eval=F}
library(tidyverse); library(magrittr);
geneticgroups<-readRDS(here::here("output","pmv_varcomps_geneticgroups.rds")) %>% 
  bind_rows(readRDS(here::here("output","pmv_DirectionalDom_varcomps_geneticgroups.rds")))
geneticgroups %<>% 
  select(-blups) %>% 
  unnest_wider(PMV) %>% 
  select(-runtime) %>% 
  unnest(pmv) %>% 
  mutate_if(is.numeric,~round(.,6)) %>% 
  pivot_longer(cols=c(VPM,PMV),names_to = "VarMethod",values_to = "Var")
```

## Compute SI variances
```{r, eval=F}
# Selection weights -----------
indices<-readRDS(file=here::here("data","selection_index_weights_4traits.rds"))
## Predicted Index Variances
geneticgroups_SI<-geneticgroups %>% 
  nest(varcovars=c(Trait1,Trait2,Var)) %>%
  mutate(varcovars=map(varcovars,
                       function(varcovars){
                         # pairwise to square symmetric matrix
                         gmat<-varcovars %>% 
                           spread(Trait2,Var) %>% 
                           column_to_rownames(var = "Trait1") %>% 
                           as.matrix %>% 
                           .[indices$Trait,indices$Trait]
                         gmat[lower.tri(gmat)]<-t(gmat)[lower.tri(gmat)]
                         return(gmat) }),
         # compute index variances
         stdSI=map_dbl(varcovars,~t(indices$stdSI)%*%.%*%indices$stdSI),
         biofortSI=map_dbl(varcovars,~t(indices$biofortSI)%*%.%*%indices$biofortSI)) %>% 
  # discard var-covar matrix
  select(-varcovars) %>% 
  pivot_longer(cols = c(stdSI,biofortSI),
               names_to = "Trait1", 
               values_to = "Var") %>% 
  mutate(Trait2=Trait1)

geneticgroups %<>% bind_rows(geneticgroups_SI)
rm(geneticgroups_SI)
```
## --> Save
```{r, eval=F}
saveRDS(geneticgroups,file=here::here("output","pmv_varcomps_geneticgroups_tidy_includingSIvars.rds"))
```

## Tidy inbreeding effect est. from DirDom model

```{r, eval=F}
library(tidyverse); library(magrittr); library(BGLR)
geneticgroups_dd<-readRDS(here::here("output","pmv_DirectionalDom_varcomps_geneticgroups.rds")) %>% 
  distinct(Group,outName) %>% 
  mutate(mtbrrFit=map(outName,~readRDS(here::here("output/mtMarkerEffects",paste0(.,".rds"))))) %>% 
  unnest_wider(mtbrrFit) %>% 
  select(-runtime,-snpIDs,-outName) %>% 
  mutate(Dataset="GeneticGroups")

parentfolds_dd<-readRDS(file = here::here("data","parentwise_crossVal_folds.rds")) %>% 
  rename(Repeat=id,Fold=id2) %>% 
  select(Repeat,Fold,trainset,testset) %>% 
  pivot_longer(c(trainset,testset),
               names_to = "Dataset",
               values_to = "sampleIDs") %>% 
  mutate(Model="DirectionalDom") %>% 
  arrange(desc(Dataset),Repeat,Fold) %>% 
  mutate(outName=paste0("mt_",Repeat,"_",Fold,"_",Dataset,"_",Model)) %>% 
  mutate(mtbrrFit=map(outName,~readRDS(here::here("output/mtMarkerEffects",paste0(.,".rds"))))) %>% 
  unnest_wider(mtbrrFit) %>% 
  select(-runtime,-snpIDs,-sampleIDs,-outName,-Model)
ddEffects<-bind_rows(geneticgroups_dd,parentfolds_dd) %>% 
  mutate(inbreff=map(mtbrrFit,function(mtbrrFit){
    traits<-colnames(mtbrrFit$yHat)
    beta<-mtbrrFit$ETA$GmeanD$beta
    SD.beta<-mtbrrFit$ETA$GmeanD$SD.beta
    colnames(beta)<-colnames(SD.beta)<-traits
    
    inbeffs<-bind_rows(as_tibble(beta),as_tibble(SD.beta)) %>% 
      t(.) %>% 
      as.data.frame %>% 
      rownames_to_column(var="Trait") %>% 
      rename(InbreedingEffect=V1,
             InbreedingEffectSD=V2)
    return(inbeffs) })) %>% 
  select(-mtbrrFit) %>% 
  unnest(inbreff)
saveRDS(ddEffects,file=here::here("output","ddEffects.rds"))
```
