---
title: "Compute observed cross means and (co)variances"
site: workflowr::wflow_site
date: "2020-June-16"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: inline
---

This step is to create validation data to which predictions of cross means and variances will be correlated. 

Compute the empirical means and variances for each validation-family: 

1. testset GEBV/GETGV of actual offspring

* VarBV_a
* VarBV_dirdom

* VarTGV_ad
* VarTGV_dirdom

2. Phenotypic BLUPs of actual offspring 

# Observed cross means and (co)vars 

## 1. Testset GBLUPs of actual offspring {#observedCrossVarsGBLUPs}

Compute the empirical means and variances for each validation-family, based on the GEBV/GETGV of actual offspring, and using the marker-effects from models fit to the test-set for each fold/rep of parent-wise cross-validation.

```{r, eval=F}
rm(list=ls());
library(tidyverse); library(magrittr); library(predCrossVar); library(BGLR);
# Testing datasets -----------
parentfolds<-readRDS(file = here::here("data","parentwise_crossVal_folds.rds")) %>% 
  rename(Repeat=id,Fold=id2) %>% 
  select(Repeat,Fold,testparents)

# Pedigree -----------
ped<-readRDS(here::here("data","ped_awc.rds")) %>%
  nest(FamilyMembers=FullSampleName)

# Crosses To Predict -------------
parentfolds %<>% 
  mutate(CrossesToPredict=map(testparents,~filter(ped,sireID %in% . | damID %in% .))) %>% 
  select(-testparents)

# Genomic BLUPs from testsets --------------
gblups<-readRDS(here::here("output","gblups_parentwise_crossVal_folds.rds")) %>% 
  filter(Dataset=="testset") %>% select(-Dataset,-outName)
gblups_dd<-readRDS(here::here("output","gblups_DirectionalDom_parentwise_crossVal_folds.rds")) %>% 
  filter(Dataset=="testset") %>% select(-Dataset,-sampleIDs) %>% 
  mutate(Model="DirDom")
gblups %<>% 
  unnest(GBLUPs) %>% 
  nest(GBLUPs=-c(Repeat,Fold,Model,predOf)) %>% 
  left_join(parentfolds)
gblups_dd %<>% 
  select(Repeat,Fold,Model,GBLUPs) %>% 
  unnest(GBLUPs) %>% 
  nest(GBLUPs=-c(Repeat,Fold,Model,predOf)) %>% 
  left_join(parentfolds)
gblups<-bind_rows(gblups,gblups_dd); 
rm(gblups_dd,parentfolds,ped)
# Selection weights -----------
indices<-readRDS(file=here::here("data","selection_index_weights_4traits.rds"))
gblups %>% count(Model,predOf)
```

### Component Traits
```{r, eval=F}
getCrossMeansAndCovs<-function(CrossesToPredict,GBLUPs,...){
  CrossesToPredict %<>%
    mutate(famgblups=map(FamilyMembers,~rename(.,germplasmName=FullSampleName) %>% 
                           left_join(GBLUPs) %>% 
                           as.data.frame %>% 
                           column_to_rownames(var = "germplasmName")),
           means=map(famgblups,~summarise_all(.,mean,na.rm=T)),
           covMat=map(famgblups,~cov(.,use='pairwise.complete.obs'))) %>% 
    select(-FamilyMembers)
  return(CrossesToPredict) 
}
```
```{r, eval=F}
realized_means_and_covs<-gblups %>% 
  mutate(observedCrossMeansAndCovs=pmap(.,getCrossMeansAndCovs)) %>% 
  select(-CrossesToPredict,-GBLUPs)
realized_means_and_covs %<>% unnest(observedCrossMeansAndCovs)
saveRDS(realized_means_and_covs,file = here::here("output/crossRealizations","realized_cross_means_and_covs_traits.rds"))
realized_means_and_covs %>% slice(1:3)
```

### Selection indices
```{r, eval=F}
realized_means_and_covs_si<-realized_means_and_covs %>% 
  mutate(meanStdSI=map_dbl(means,~as.matrix(.)%*%indices$stdSI),
         meanBiofortSI=map_dbl(means,~as.matrix(.)%*%indices$biofortSI),
         varStdSI=map_dbl(covMat,~indices$stdSI%*%as.matrix(.)%*%indices$stdSI),
         varBiofortSI=map_dbl(covMat,~indices$biofortSI%*%as.matrix(.)%*%indices$biofortSI)) %>% 
  select(-famgblups,-means,-covMat)
saveRDS(realized_means_and_covs_si,file = here::here("output/crossRealizations","realized_cross_means_and_vars_selindices.rds"))
realized_means_and_covs_si %>% slice(1:3)
```

### Tidy

Tidy / format the realized cross means and variances.  
Combine traits and sel. indices. Split into two separate tibbles, one for means, one for variances.  
Output will be ready to combine with predictions to measure accuracy.

```{r, eval=F}
library(tidyverse); library(magrittr);
realized_means_and_covs_traits<-readRDS(here::here("output/crossRealizations","realized_cross_means_and_covs_traits.rds"))
realized_means_and_covs_si<-readRDS(here::here("output/crossRealizations","realized_cross_means_and_vars_selindices.rds"))
```

#### Realized means
```{r, eval=F}
# Means ---------------
## Traits
realized_means_traits<-realized_means_and_covs_traits %>% 
  select(Repeat,Fold,Model,predOf,sireID,damID,means) %>% 
  unnest(means) %>% 
  pivot_longer(cols = c(-Repeat,-Fold,-Model,-predOf,-sireID,-damID),names_to = "Trait", values_to = "obsMean") %>% 
  mutate(obsOf=ifelse(predOf=="BV","MeanBV","MeanTGV")) %>% 
  select(-predOf) 
## SIs
realized_means_si<-realized_means_and_covs_si %>% 
  select(Repeat,Fold,Model,predOf,sireID,damID,contains("mean")) %>% 
  rename(stdSI=meanStdSI,
         biofortSI=meanBiofortSI) %>% 
  pivot_longer(cols = c(-Repeat,-Fold,-Model,-predOf,-sireID,-damID),names_to = "Trait", values_to = "obsMean") %>% 
  mutate(obsOf=ifelse(predOf=="BV","MeanBV","MeanTGV")) %>% 
  select(-predOf)
## Combine
realized_means<-bind_rows(realized_means_si,realized_means_traits)
rm(realized_means_traits,realized_means_si)
realized_means %>% count(Model,obsOf) %>% spread(obsOf,n)
```
#### Realized (co)variances
```{r, eval=F}
# (Co)variances -------------
## Traits
realized_vars_traits<-realized_means_and_covs_traits %>% 
  select(Repeat,Fold,Model,predOf,sireID,damID,covMat) %>% 
  mutate(covMat=map(covMat,function(covMat){
    covMat[lower.tri(covMat, diag = F)]<-NA
    covMat %<>% 
      as.data.frame %>% 
      rownames_to_column(var = "Trait1") %>% 
      pivot_longer(cols = -Trait1, names_to = "Trait2", values_to = "obsVar",values_drop_na = TRUE)
    return(covMat)})) %>% 
  unnest(covMat) %>% 
  mutate(obsOf=ifelse(predOf=="BV","VarBV","VarTGV")) %>% 
  select(-predOf) 
## SIs
realized_vars_si<-realized_means_and_covs_si %>% 
  select(Repeat,Fold,Model,predOf,sireID,damID,contains("var")) %>% 
  rename(stdSI=varStdSI,
         biofortSI=varBiofortSI) %>% 
  pivot_longer(cols = c(-Repeat,-Fold,-Model,-predOf,-sireID,-damID),names_to = "Trait1", values_to = "obsVar") %>% 
  mutate(obsOf=ifelse(predOf=="BV","VarBV","VarTGV"),
         Trait2=Trait1) %>% 
  select(-predOf)
## Combine
realized_vars<-bind_rows(realized_vars_si,realized_vars_traits)
                          # rename(obsVar=VarSCA))
rm(realized_vars_si,realized_vars_traits)
realized_vars %>% count(Model,obsOf) %>% spread(obsOf,n)
```

#### --> Save
```{r, eval=F}
saveRDS(realized_means,here::here("output/crossRealizations","realizedCrossMeans.rds"))
saveRDS(realized_vars,here::here("output/crossRealizations","realizedCrossVars.rds"))
```

## 2. Phenotypic BLUPs of actual offspring{#observedCrossVarsiidBLUPs}
```{r, eval=F}
rm(list=ls());
library(tidyverse); library(magrittr); library(predCrossVar); library(BGLR);
# Testing datasets -----------
parentfolds<-readRDS(file = here::here("data","parentwise_crossVal_folds.rds")) %>% 
  rename(Repeat=id,Fold=id2) %>% 
  select(Repeat,Fold,testparents)

# Pedigree -----------
ped<-readRDS(here::here("data","ped_awc.rds")) %>%
  nest(FamilyMembers=FullSampleName)

# Crosses To Predict -------------
parentfolds %<>% 
  mutate(CrossesToPredict=map(testparents,~filter(ped,sireID %in% . | damID %in% .))) %>% 
  select(-testparents)

# Selection weights -----------
indices<-readRDS(file=here::here("data","selection_index_weights_4traits.rds"))

# BLUPs -----------
blups<-readRDS(here::here("data","blups_forawcdata.rds")) %>% 
  select(Trait,blups) %>% 
  unnest(blups) %>% 
  select(Trait,germplasmName,BLUP) %>% 
  spread(Trait,BLUP)

crossblups<-parentfolds %>% 
  unnest(CrossesToPredict) %>% 
  distinct(sireID,damID,FamilyMembers) %>% 
  unnest(FamilyMembers) %>% 
  rename(germplasmName=FullSampleName) %>% 
  left_join(blups) %>% 
  select(sireID,damID,germplasmName,all_of(indices$Trait)) %>% 
  nest(famblups=c(germplasmName,all_of(indices$Trait))) %>% 
  mutate(stdSI=map(famblups,~as.data.frame(.) %>% 
                       column_to_rownames(var = "germplasmName") %>% 
                       as.matrix(.)%*%indices$stdSI),
         biofortSI=map(famblups,~as.data.frame(.) %>% 
                       column_to_rownames(var = "germplasmName") %>% 
                       as.matrix(.)%*%indices$biofortSI))
# Cross Means
crossmeans<-crossblups %>% 
  mutate(means=map(famblups,~summarize_if(.,is.numeric,mean,na.rm=T))) %>% 
  unnest(means) %>% 
  mutate(stdSI=map_dbl(stdSI,mean,na.rm=T),
         biofortSI=map_dbl(biofortSI,mean,na.rm=T)) %>% 
  select(-famblups) %>% 
  pivot_longer(cols = c(-sireID,-damID), names_to = "Trait", values_to = "obsMean", values_drop_na = TRUE)
# Cross (Co)Vars
crossvars<-crossblups %>% 
  mutate(varcovars=map(famblups,~cov(as.data.frame(.) %>% 
                                       column_to_rownames(var = "germplasmName") %>% 
                                       as.matrix, 
                                     use = 'pairwise.complete.obs')),
         varcovars=map(varcovars,function(varcovars){
           varcovars[lower.tri(varcovars, diag = F)]<-NA
           varcovars %<>% 
             as.data.frame %>% 
             rownames_to_column(var = "Trait1") %>% 
             pivot_longer(cols = -Trait1, names_to = "Trait2", values_to = "obsVar",values_drop_na = TRUE)
           return(varcovars)})) %>% 
  select(-famblups,-stdSI,-biofortSI) %>% 
  unnest(varcovars)
crossvars<-bind_rows(crossvars,crossblups %>% 
                       mutate(stdSI=map_dbl(stdSI,var,na.rm=T),
                              biofortSI=map_dbl(biofortSI,var,na.rm=T)) %>% 
                       select(-famblups) %>% 
                       pivot_longer(cols = c(-sireID,-damID), names_to = "Trait1", values_to = "obsVar", values_drop_na = TRUE) %>% 
                       mutate(Trait2=Trait1))
```

#### --> Save
```{r, eval=F}
saveRDS(crossmeans,here::here("output/crossRealizations","realizedCrossMeans_BLUPs.rds"))
saveRDS(crossvars,here::here("output/crossRealizations","realizedCrossVars_BLUPs.rds"))
```

# Measures of Post-cross Selection {#realIntensity}

## Metrics as parents

For each family, compute the proportion of offspring subsequently used as parents.  

Compute the realized "Usefulness" of the cross in terms of population improvement / parent-development as the mean GEBV of family members that are themselves parents. 

```{r, eval=F}
library(tidyverse); library(magrittr); library(predCrossVar)
indices<-readRDS(here::here("data","selection_index_weights_4traits.rds"))
realized_means_and_covs<-readRDS(here::here("output/crossRealizations","realized_cross_means_and_covs_traits.rds"))

ped<-readRDS(here::here("data","ped_awc.rds"))
parents<-union(ped$sireID,ped$damID)

realized_cross_gebvs_si<-realized_means_and_covs %>% 
  filter(predOf=="BV") %>% 
  mutate(stdSI=map(famgblups,~as.matrix(.)%*%indices$stdSI),
         biofortSI=map(famgblups,~as.matrix(.)%*%indices$biofortSI),
         GEBV=map2(stdSI,biofortSI,~tibble(germplasmName=rownames(.x),stdSI=.x,biofortSI=.y))) %>% 
  select(-famgblups,-means,-covMat,-stdSI,-biofortSI)

realizedparentmetrics<-realized_cross_gebvs_si %>% 
  unnest(GEBV) %>% 
  mutate(IsParent=ifelse(germplasmName %in% parents,TRUE,FALSE)) %>% 
  nest(Family=c(germplasmName,IsParent,stdSI,biofortSI)) 

realizedparentmetrics %<>% 
  mutate(FamSize=map_dbl(Family,nrow),
         NmembersUsedAsParent=map_dbl(Family,~length(which(.$IsParent==TRUE))),
         propUsedAsParent=map_dbl(Family,~length(which(.$IsParent==TRUE))/nrow(.)),
         realizedUCparent_stdSI=map_dbl(Family,~mean(.$stdSI[.$IsParent==TRUE],na.rm = T)),
         realizedUCparent_biofortSI=map_dbl(Family,~mean(.$biofortSI[.$IsParent==TRUE],na.rm = T)),
         # also compute the mean of top 1% of the family
         # correspond ~std. intensity = 2.67
         # provides alternative validation data for usefulness criteria
         # invariant to actual selection intensity 
         meanTop1pctGEBV_stdSI=map_dbl(Family, ~slice_max(.data = .,
                                                          order_by = stdSI, 
                                                          n=ceiling(0.01*nrow(.))) %$% mean(stdSI)),
         meanTop1pctGEBV_biofortSI=map_dbl(Family, ~slice_max(.data = .,
                                                              order_by = biofortSI, 
                                                              n=ceiling(0.01*nrow(.))) %$% mean(biofortSI))) %>% 
  select(-Family) %>% 
  ungroup()
rm(realized_cross_gebvs_si)
```

## Metrics as varieties

For each family, compute the proportion of offspring that have been advanced on the variety development pipeline (VDP) to different stages. 

Compute the stage-specific "Usefulness" of the cross in terms of variety development as the mean GETGV of family members advanced to each stage.
```{r, eval=F}
# Read for web the raw plot-data used as of summer 2019 for IITA GS
trials<-readRDS(url("https://raw.github.com/wolfemd/IITA_2019GS/master/data/IITA_ExptDesignsDetected_72619.rds"))
realizedVDPmetrics<-ped %>% 
  rename(GID=FullSampleName) %>% 
  left_join(trials %>% 
              filter(Trait %in% indices$Trait) %>% 
              unnest_legacy(TrialData) %>% 
              select(germplasmName,observationUnitDbId,TrialType) %>% 
              distinct %>% 
              count(germplasmName,TrialType,name = "Nplots") %>% 
              filter(TrialType %in% c("GeneticGain","CET","ExpCET","PYT","AYT","UYT")) %>% 
              rename(GID=germplasmName) %>% 
              spread(TrialType,Nplots) %>% 
              select(c("GID","GeneticGain","CET","ExpCET","PYT","AYT","UYT"))) %>% 
  mutate(IsPhenotyped=rowSums(.[,c("GeneticGain","CET","ExpCET","PYT","AYT","UYT")],na.rm = T)>0,
         advancedPastCET=rowSums(.[,c("GeneticGain","PYT","AYT","UYT")],na.rm = T)>0,
         advancedPastPYT=rowSums(.[,c("GeneticGain","AYT","UYT")],na.rm = T)>0,
         advancedPastAYT=rowSums(.[,c("GeneticGain","UYT")],na.rm = T)>0) %>% 
  select(-c("GeneticGain","CET","ExpCET","PYT","AYT","UYT")) %>% 
  rename(germplasmName=GID)
realized_cross_getgvs_si<-realized_means_and_covs %>% 
  filter(predOf=="TGV") %>% 
  mutate(stdSI=map(famgblups,~as.matrix(.)%*%indices$stdSI),
         biofortSI=map(famgblups,~as.matrix(.)%*%indices$biofortSI),
         GETGV=map2(stdSI,biofortSI,~tibble(germplasmName=rownames(.x),stdSI=.x,biofortSI=.y))) %>% 
  select(-famgblups,-means,-covMat,-stdSI,-biofortSI)
realizedVDPmetrics<-realized_cross_getgvs_si %>% 
  unnest(GETGV) %>% 
  left_join(realizedVDPmetrics) %>% 
  nest(data=c(germplasmName,stdSI,biofortSI,IsPhenotyped,contains("advancedPast"))) %>% 
  mutate(FamSize=map_dbl(data,nrow),
         NmembersPhenotyped=map_dbl(data,~length(which(.$IsPhenotyped==TRUE))),
         NmembersPastCET=map_dbl(data,~length(which(.$advancedPastCET==TRUE))),
         NmembersPastPYT=map_dbl(data,~length(which(.$advancedPastPYT==TRUE))),
         NmembersPastAYT=map_dbl(data,~length(which(.$advancedPastAYT==TRUE))),
         propPhenotyped=map_dbl(data,~length(which(.$IsPhenotyped==TRUE))/nrow(.)),
         propPastCET=map_dbl(data,~length(which(.$advancedPastCET==TRUE))/nrow(.)),
         propPastPYT=map_dbl(data,~length(which(.$advancedPastPYT==TRUE))/nrow(.)),
         propPastAYT=map_dbl(data,~length(which(.$advancedPastAYT==TRUE))/nrow(.)),
         realizedUCatCET_stdSI=map_dbl(data,~mean(.$stdSI[.$IsPhenotyped==TRUE],na.rm = T)),
         realizedUCatPYT_stdSI=map_dbl(data,~mean(.$stdSI[.$advancedPastCET==TRUE],na.rm = T)),
         realizedUCatAYT_stdSI=map_dbl(data,~mean(.$stdSI[.$advancedPastPYT==TRUE],na.rm = T)),
         realizedUCatUYT_stdSI=map_dbl(data,~mean(.$stdSI[.$advancedPastAYT==TRUE],na.rm = T)),
         realizedUCatCET_biofortSI=map_dbl(data,~mean(.$biofortSI[.$IsPhenotyped==TRUE],na.rm = T)),
         realizedUCatPYT_biofortSI=map_dbl(data,~mean(.$biofortSI[.$advancedPastCET==TRUE],na.rm = T)),
         realizedUCatAYT_biofortSI=map_dbl(data,~mean(.$biofortSI[.$advancedPastPYT==TRUE],na.rm = T)),
         realizedUCatUYT_biofortSI=map_dbl(data,~mean(.$biofortSI[.$advancedPastAYT==TRUE],na.rm = T)),
         # also compute the mean of top 1% of the family
         # correspond ~std. intensity = 2.67
         # provides alternative validation data for usefulness criteria
         # invariant to actual selection intensity 
         meanTop1pctGETGV_stdSI=map_dbl(data, ~slice_max(.data = .,
                                                          order_by = stdSI, 
                                                          n=ceiling(0.01*nrow(.))) %$% mean(stdSI)),
         meanTop1pctGETGV_biofortSI=map_dbl(data, ~slice_max(.data = .,
                                                              order_by = biofortSI, 
                                                              n=ceiling(0.01*nrow(.))) %$% mean(biofortSI))) %>% 
  select(-data) %>% 
  ungroup()
rm(realized_cross_getgvs_si,trials)
```
Combine parent + variety metrics
```{r, eval=F}
realizedcrossmetrics<-left_join(realizedparentmetrics %>% 
                                  select(-predOf) %>% 
                                  mutate(Model=ifelse(Model=="A","ClassicAD",Model)),
                                realizedVDPmetrics %>% 
                                  select(-predOf) %>% 
                                  mutate(Model=ifelse(Model=="AD","ClassicAD",Model))) %>% 
  ungroup()
```

## Realized intensities

To compare realized and predicted "usefulness criteria", we need to compute the realized, standardized selection intensity. 

1. For pop improve / UC_parent: prop of family members used as parents
2. For variety devel / UC_variety: prop of family members advanced >SDN, >CET, >PYT, >AYT

Compute the standrardized selection intensity from the proportion selected. 
This will give NaN for propSel==0. Progeny as crosses with NaN UC were never themselves used as parents. Their "usefulness" has not be "observed" / "evaluated".

```{r, eval=F}
realizedcrossmetrics %<>%
  mutate(realIntensityParent=map_dbl(propUsedAsParent,intensity),
         realIntensityCET=map_dbl(propPhenotyped,intensity),
         realIntensityPYT=map_dbl(propPastCET,intensity),
         realIntensityAYT=map_dbl(propPastPYT,intensity),
         realIntensityUYT=map_dbl(propPastAYT,intensity))
```

## --> Save
```{r, eval=F}
saveRDS(realizedcrossmetrics,file=here::here("output/crossRealizations","realizedCrossMetrics.rds"))
```

